CRUSE to Safe Cycling in Ireland

### 2023-09-13 paper.qmd
Post merge fixes
FYI made a few typo fixes @temospena, thanks for the quick and concise contribution : )

The first version of the PCT was based solely on current and future potential uptake of cycling for single stage travel to work at desire line, zone, route, and route network levels [@lovelace2016].
It was launched in April 2017 as the government-endorsed tool for strategic cycle network planning, as part of the Cycling and Walking Investment Strategy [@cycling2017].
Extensions of the PCT approach have included estimation of benefits at the individual level [@woodcock2018], addition of travel to school network [@goodman2019], and improvement modelling of impacts on health, environmental and distributional outcomes [@woodcock2021].

>>>>

The first version of the PCT was based solely on current and future potential uptake of cycling for single stage travel to work at desire line, zone, route, and route network levels [@lovelace2016].
It was launched in April 2017 as the government-endorsed tool for strategic cycle network planning, as part of the Cycling and Walking Investment Strategy [@cycling2017].
Extensions of the PCT approach have included estimation of benefits at the individual level [@woodcock2018], addition of travel to school network [@goodman2019], and improvement modelling of impacts on health, environmental and distributional outcomes [@woodcock2021].
In Portugal, a cycling uptake tool to support decision making was developed based on PCT methods, for the Lisbon metro region (see [biclaR](https://biclar.tmlmobilidade.pt), and again, social and environment impacts were added as a relevant information to support decisions, using the WHO HEAT for Cycling tool[^3] [@felix2023]. biclaR added on the previous methods by setting an 'intermodality' scenario that combines cycling with currently available public transit options based on General Transit Feed Specification (GTFS) data.

[^3]: See the Health economic assessment tool for walking and cycling at [www.heatwalkingcycling.org](https://www.heatwalkingcycling.org/#homepage).
